### 2019-11-13 latex/vhcs.tex
Created minipage for D_psi and V_psi

To see this, suppose the constrained dynamics had Lagrangian given by
\begin{equation*}
   \mathcal{L}_{\Psi}(s,\dot{s}) = \frac{1}{2}
   D_{\Psi}(s)\dot{s}^2 + V_{\Psi}(s)
\end{equation*}
where \(D_{\Psi} : \Theta \rightarrow \mathbb{R}_{>0}\) is the virtual mass
and \(V_{\Psi} : \Theta \rightarrow \mathbb{R}\) is the virtual potential of the
system. Then the equations of motion of this system are
\begin{equation*}
   D_{\Psi}'(s)\dot{s}^2 + D_{\Psi}(s)\ddot{s} - \frac{1}{2}D_{\Psi}'(s)\dot{s}
   + V_{\Psi}'(s) = 0
\end{equation*}
\begin{equation}\label{eqn:lagrangian_constrained_dynamics_general}
   \Rightarrow \ddot{s} = -\frac{V_{\Psi}'(s)}{D_{\Psi}(s)} -
   \frac{D_{\Psi}'(s)}{2 D_{\Psi}(s)}
\end{equation}

Setting (\ref{eqn:lagrangian_constrained_dynamics}) and
(\ref{eqn:lagrangian_constrained_dynamics_general}) equal to each other, one
can compute the values of \(D_{\Psi}\) and \(V_{\Psi}\). First, one sees that
\(V_{\Psi}(s)\) is defined by \(D_{\Psi}\) and \(\Psi_1\):
\begin{align*}
   \Psi_1(s) &= -\frac{V_{\Psi}'(s)}{D_{\Psi}(s)} \\
   \Rightarrow V_{\Psi}'(s) &= -D_{\Psi}(s) \Psi_1(s) \\
   \Rightarrow V_{\Psi}(s) &= - \int \limits_{0}^s
   D_{\Psi}(\tau)\Psi_1(\tau)d\tau
\end{align*}
where \(D_{\Psi}\) is given by
\begin{align*}
   \Psi_2(s) &= -\frac{D_{\Psi}'(s)}{D_\Psi(s)} \\
   \Rightarrow D_{\Psi}'(s) &= -D_{\Psi}(s) \Psi_2(s) \\
   \Rightarrow D_{\Psi}(s) &= \exp\left[ 
   -2\int \limits_{0}^s \Psi_2(\tau) d\tau \right]
\end{align*}

@@

\subsection{Hamiltonian Virtual Nonholonomic Constraints}

>>>>

To see this, suppose the constrained dynamics had Lagrangian given by
\begin{equation}\label{eqn:vhcs_constrained_lagrangian}
   \mathcal{L}_{\Psi}(s,\dot{s}) = \frac{1}{2}
   D_{\Psi}(s)\dot{s}^2 + V_{\Psi}(s)
\end{equation}
where \(D_{\Psi} : \Theta \rightarrow \mathbb{R}_{>0}\) is the virtual mass
and \(V_{\Psi} : \Theta \rightarrow \mathbb{R}\) is the virtual potential of the
system. Then the equations of motion of this system are
\begin{equation*}
   D_{\Psi}'(s)\dot{s}^2 + D_{\Psi}(s)\ddot{s} - \frac{1}{2}D_{\Psi}'(s)\dot{s}
   + V_{\Psi}'(s) = 0
\end{equation*}
\begin{equation}\label{eqn:lagrangian_constrained_dynamics_general}
   \Rightarrow \ddot{s} = -\frac{V_{\Psi}'(s)}{D_{\Psi}(s)} -
   \frac{D_{\Psi}'(s)}{2 D_{\Psi}(s)}
\end{equation}

Setting (\ref{eqn:lagrangian_constrained_dynamics}) and
(\ref{eqn:lagrangian_constrained_dynamics_general}) equal to each other, one
can compute the values of \(D_{\Psi}\) and \(V_{\Psi}\): 
% Empty line here required for spacing

\begin{minipage}{0.48\textwidth}
\begin{align*}
   \Psi_2(s) &= -\frac{D_{\Psi}'(s)}{D_\Psi(s)} \\
   \Rightarrow D_{\Psi}'(s) &= -D_{\Psi}(s) \Psi_2(s) \\
   \Rightarrow D_{\Psi}(s) &= \exp\left[ 
   -2\int \limits_{0}^s \Psi_2(\tau) d\tau \right]
\end{align*}
\end{minipage}
% No empty lines between these
\begin{minipage}{0.48\textwidth}
\begin{align*}
   \Psi_1(s) &= -\frac{V_{\Psi}'(s)}{D_{\Psi}(s)} \\
   \Rightarrow V_{\Psi}'(s) &= -D_{\Psi}(s) \Psi_1(s) \\
   \Rightarrow V_{\Psi}(s) &= - \int \limits_{0}^s
   D_{\Psi}(\tau)\Psi_1(\tau)d\tau
\end{align*}
\end{minipage}

Thus, the constrained dynamics for mechanical systems are Euler-Lagrange with
Lagrangian (\ref{eqn:vhcs_constrained_lagrangian}).

@@

\subsection{Hamiltonian Virtual Nonholonomic Constraints}
While VHCs are still possible in the Hamiltonian framework, the assumptions
required to make this work are slightly different. To see this, let us look back
to the derivation which led to the error dynamics (\ref{eqn:vhc_error_dynamics})
and attempt to reconstruct this in Hamiltonian coordinates.
